Paper Analysis

### 2025-04-25 Paper_WriteUp/Paper_Plots.qmd
using the rating in current simulation in ppd. Also using newer history calculation

#adding performance history
init_data = tidy_games |>
  mutate(WhiteElo = as.numeric(WhiteElo),
         BlackElo = as.numeric(BlackElo),
         focal_user = ifelse(focal_white == 1, White, Black),
         elo_diff = ifelse(focal_white == 1,
                           WhiteElo - BlackElo, BlackElo - WhiteElo),
         focal_id = match(focal_user, users),
         focal_rating = ifelse(focal_white == 1, WhiteElo, BlackElo),
         opp = ifelse(focal_white == 1, Black, White),
         opp_rating = ifelse(focal_white == 1, BlackElo, WhiteElo),
         UTCDateTime = ymd_hms(paste0(UTCDate, "_", UTCTime))) |>
  dplyr::select(focal_user, focal_id, focal_white, WhiteElo, BlackElo,
                focal_win_prop, elo_diff, focal_result, opp, opp_rating,
                focal_rating, UTCDateTime) |>
  group_by(focal_id) |>
  mutate(time_diff = UTCDateTime - lag(UTCDateTime, default = NA), 
         ave_prop = ifelse(time_diff <= 300,  #if games played in diff sessions, make history same as draw (ie NULL)
                           lag(focal_win_prop, default = 0.5), #removing standardization
                           0.5)) |>
  ungroup() |>
  filter(focal_result != 0.5)

@@

## the covariates for the future games
future_games_cov = tibble(focal = as.character(focal_init_data$focal_id),  
                          color = focal_init_data$focal_white,
                          elo_diff = focal_init_data$elo_diff,
                          hist = focal_init_data$ave_prop,
                          focal_rating = focal_init_data$focal_rating,
                          opponent = focal_init_data$opp,
                          opponent_rating = focal_init_data$opp_rating)

@@

  #elo diff for rating effect
  rating_diff = curr_game_info$elo_diff

@@

  #simulate wins/loss on current game
  for (j in 1:num_sims) {
    curr_draw = focal_draws %>% filter(draw == j)

@@

>>>>

init_data <- tidy_games |>
  mutate(WhiteElo = as.numeric(WhiteElo),
         BlackElo = as.numeric(BlackElo),
         focal_user = ifelse(focal_white == 1, White, Black),
         elo_diff = ifelse(focal_white == 1,
                           WhiteElo - BlackElo, BlackElo - WhiteElo),
         focal_id = match(focal_user, users),
         focal_rating = ifelse(focal_white == 1, WhiteElo, BlackElo),
         opp = ifelse(focal_white == 1, Black, White),
         opp_rating = ifelse(focal_white == 1, BlackElo, WhiteElo),
         UTCDateTime = ymd_hms(paste0(UTCDate, "_", UTCTime))) |>
  dplyr::select(focal_user, focal_id, focal_white, WhiteElo, BlackElo,
                focal_win_prop, elo_diff, focal_result, opp, opp_rating,
                focal_rating, UTCDateTime) |>
  group_by(focal_id) |>
  mutate(time_diff = UTCDateTime - lag(UTCDateTime, default = NA), #default is to ensure first game is always start of a new session
         cum_win_prob = cummean(focal_result), #the mean win probability for the focal player up to the ith (current) game 
         ave_prop = ifelse(time_diff > 300 | is.na(time_diff),  
                           cum_win_prob, #if games played in different session, history is their mean win prob up to the current game
                           lag(focal_win_prop))) |> #if game played in same session, rolling mean over the past n games, removing standardization 
  filter(focal_result != 0.5) %>%
  ungroup()

@@

## the covariates for the future games
future_games_cov = tibble(focal = as.character(focal_init_data$focal_id),  
                          color = focal_init_data$focal_white,
                          elo_diff = focal_init_data$elo_diff,
                          focal_result = focal_init_data$focal_result,
                          hist = focal_init_data$ave_prop,
                          focal_rating = focal_init_data$focal_rating,
                          opponent = focal_init_data$opp,
                          opponent_rating = focal_init_data$opp_rating)

@@

@@

  #simulate wins/loss on current game
  for (j in 1:num_sims) {
    curr_draw = focal_draws %>% filter(draw == j) #current draw of parameters

@@

  #rating diff in current game in jth simulation
  rating_diff = curr_rating - opp_rating
